\documentclass{article}

\input{preamble}

\begin{document}

\thispagestyle{empty}

\header{Daniel Öman}{dsoman24@gmail.com}{(470) 553-5299}{Atlanta, GA}{dsoman24}{daniel-s-oman}

\begin{flushleft}

\sectitle{Education}

\school{Georgia Institute of Technology}{August 2021 -- May 2025 (expected)}
{\textbf{\textit{B.S. Computer Science, concentrations in Intelligence (AI/ML) and Theory}} \hfill 3.96/4.0 GPA \\ \textit{Relevant Courses}:
    Data Structures \& Algorithms,
    Machine Learning,
    Deep Learning,
    Computer Organization \& Programming
    % Objects \& Design,
    %Automata \& Complexity,
    %Number Theory%,
    %Graduate Algorithms*
    %\textit{(* = current)}
    \\
    % \textit{Activities}: Delta Chi Fraternity (Secretary, Professional Development Chair), Society of Hispanic Professional Engineers
}

\sectitle{Experience}

    \begin{experience}{Ditch}{Atlanta, GA}{Software Engineering Intern}{September 2024 -- Present}
        \item Develop and launch new features for a fast-growing early-stage fintech startup's flagship mobile app with 3k+ users automating \$100k+ in debt repayment, by using Flutter/Dart for the frontend and Python with GCP Run Functions for the backend.
        \item Implement custom recommendation systems leveraging Python, Firebase PostgreSQL, and OpenAI LLM APIs to provide users with personalized app experiences, leading to a decrease in user churn by 20\% and an increase in user engagement by 30\%.
    \end{experience}

    \begin{experience}{Google}{Kirkland, WA}{Software Engineering Intern}{May 2024 -- August 2024}
        \item Designed and implemented a distributed load testing framework in C++ and Python to benchmark the scalability of a streaming metadata change-log service within Google BigQuery's core infrastructure.
        \item Designed continuous test runs as a custom development \& monitoring workflow, reducing regressions by 70\% before production.
        \item Developed a load sampling system simulating 10k+ requests/sec to identify bottlenecks in the service's read/write RPC endpoints.
        \item Built a multi-threaded C++ measurement system to analyze latency, throughput, and error rates, improving test accuracy by 50\%.
        \item Led efforts to fix a critical SLO bug in the storage metadata server, eliminating error spikes by 90\% with request retry logic.
    \end{experience}

    \begin{experience}{Georgia Tech Efficient and Intelligent Computing Lab}{Atlanta, GA}{Undergraduate Research Assistant}{January -- May 2024}
        \item Contributed to a PyTorch toolkit used by 5+ Georgia Tech labs to train distributed Graph Neural Networks (GNNs) for applications with multiple large disjoint graphs, such as electronic design analysis and molecular modeling.
        \item Developed a modular data loading and transfer API and implemented GraphSAGE, improving model accuracy by 15\%.
    \end{experience}

    \begin{experience}{Georgia Tech College of Computing}{Atlanta, GA}{Undergraduate Teaching Assistant (Homework Lead)}{August 2022 -- May 2024}
        \item Managed a team of 40 TAs in the development and grading of 12 homework assignments for over 800 students per semester as TA Homework Lead for CS 1331: Intro to Object-Oriented Programming (Java) under Prof.~Richard Landry and Dr.~Aibek Musaev.
        \item Led weekly recitations for 50 students; held 1-1 office hours 3 times a week to aid students with problem-solving and debugging.
    \end{experience}

    \begin{experience}{Google}{Sunnyvale, CA}{Software Engineering (STEP) Intern}{May -- August 2023}
        \item Designed and implemented an efficient parallel data pipeline for production use, generating 70+ features to train ML models predicting Google Workspace upgrade, downgrade, and churn behaviors.
        \item Built pipeline using FlumeJava, a Java MapReduce framework, to extract and aggregate domain level ML features from a 500B+ webpage database, increasing customer coverage in the feature store by 20\%.
        \item Engineered a scalable data aggregation architecture using advanced OOP patterns, reducing feature implementation time by 50\% and provided an intuitive code interface for future feature store contributions.
        \item Improved pipeline reliability by developing a system to flush intermediate output from 10k+ processes to Spanner, preventing up to 7 days of data loss during full table scans.
    \end{experience}

    \sectitle{Projects}

    \vspace{3pt}

    \begin{project}{Hemodynamics Calculator}{https://github.com/dsoman24/hemodynamics-calculator}{JavaScript, ReactJS, MongoDB, Express, NodeJS}{August 2023 -- April 2024}
        \item Developed a full-stack app used by 10+ ICU clinicians, reducing blood flow measurement errors for 1,000+ patients annually.
        \item Placed 3rd out of 50 teams in the Georgia Tech CS Capstone Expo, presenting to 40+ industry professionals and professors.
    \end{project}

    % \begin{project}{Machine Learning Soccer Prediction}{https://dsoman24.github.io/ml-project/}{Python, Scikit-Learn, PyTorch, NumPy, Matplotlib, Seaborn}{August -- December 2023}
    %     \item Worked on a team of 5 to build and train logistic regression, random forest, and artificial neural network models using Scikit-Learn and PyTorch to predict soccer match outcomes with 70\% accuracy, beating benchmark betting odds data by 8\%.
    %     \item Built feature engineering strategies and conducted hyperparameter tuning to reduce overfitting, improving accuracy by $\sim$10\%.
    % \end{project}

    \begin{project}{Deep Learning Song Recommender}{https://dsoman24.github.io/}{Python, PyTorch, NumPy}{August 2024 -- Present}
        \item Develop a multimodal deep learning model to recommend songs using audio, lyrics, and user history, trained on 1M+ songs.
        \item Leverage CNNs, pretrained BERT, and a DNN to generate embeddings, achieving 80\% accuracy in predicting preferences.
    \end{project}

\sectitle{Skills}

    \vspace{3pt}
    \skill{Programming Languages}{Java, C/C++, Python, SQL, Dart, JavaScript, \LaTeX} \\
    \skill{Frameworks}{FlumeJava (MapReduce), JUnit, NumPy, Pandas, Scikit-Learn, PyTorch, ReactJS, Express, NodeJS, Flutter, Flask} \\
    \skill{Tools}{Git, Mercurial, Bazel, Protobuf, GCP, gRPC, Spanner, MySQL, PostgreSQL, MongoDB} \\

\end{flushleft}

\end{document}